\documentclass[11pt,a4paper]{lettre}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[
    english,
    francais
    ]{babel}
\usepackage{fourier}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{hmargin=2.5cm,vmargin=1.5cm}
%\def\concname{\hspace{-1.5cm}:~}


\begin{document}
\begin{letter} 
{OUTSCALE  \\
%{address}\\
92~210 
Saint-Cloud }
\selectlanguage{english}   
\name{Mr.  Gaya \textsc{Benane}}\\
\address{Gaya \textsc{Benane}\\ 171 avenue de Luminy\\ 13~009~Marseille}  

\signature{Gaya \textsc{Benane}}
\lieu{Marseille}
\nofax
\date{\today}
\telephone{ +33~(0)~668~056~437 }
\email{\href{mailto:gaya.benane@outlook.fr}{gaya.benane@outlook.fr}}

    %\vfill
\conc{\textbf{Job application for a Data Scientist position}}
%\opening{\hspace{1em} Dear Hiring Manager,}
\opening{\hspace{1em} Dear Ismaël \textsc{Prigent},}
\hspace{1em}
I am excited to submit my application for the Data Scientist position at OUTSCALE as advertised in \href{https://www.apec.fr}{Apec website} with reference number 173574500. My journey through a Ph.D. in Particle Physics, enhanced by a solid foundation in mathematics and physics, has equipped me with a deep analytical mindset and exceptional problem-solving skills.

\hspace{1em}
During my academic and research tenure, I specialized in particle physics, where I mastered statistical analysis, data visualization, and the development of sophisticated simulation models—key competencies for a Data Scientist. My ability to extract patterns and insights from large datasets is directly applicable to the challenges in data science.
My education at École Polytechnique ($\ell$’X), with its rigorous curriculum and focus on innovation, further strengthened my skills in applied mathematics and computer science. This experience instilled in me a balanced approach of creativity and analytical rigor, crucial for advancing in artificial intelligence.

I am thrilled to apply for the Data Scientist position at OUTSCALE, part of Dassault Systèmes, to contribute to the Business Experience team. With my experience during my thesis,  
I bring a foundational understanding of data science, reinforced by hands-on projects involving Python and ML/DL frameworks like Pytorch. 
I am particularly interested in both supervised and unsupervised learning contexts. I have initial exposure to cloud environments, which I am keen to expand upon. I am particularly attracted to OUTSCALE's vision of creating a sustainable and inclusive digital world, and I am motivated by the opportunity to grow within an innovative team that prizes curiosity and teamwork. Joining OUTSCALE means not only advancing my skills but also contributing to a collective mission of developing trusted technological solutions for a better future.
\closing{\hspace{1em}
I am enthusiastic about the possibility of becoming an active member of OUTSCALE, contributing significantly to your team's efforts to develop trusted technological solutions for a better future. Thank you for considering my application. I look forward to discussing how my background, skills, and passion align with the needs of your team.
}
\end{letter}
\end{document}
