\documentclass[11pt,a4paper]{lettre}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[
    english,
    francais
    ]{babel}
\usepackage{fourier}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{hmargin=2.5cm,vmargin=2cm}
%\def\concname{\hspace{-1.5cm}:~}


\begin{document}
\begin{letter} 
{\textsc{Probayes}  \\
%{address}\\
%{codepostal} 
\textsc{Montbonnot-Saint-Martin} }
\selectlanguage{english}   
\name{{ Mr Gaya \textsc{Benane} }}
\address{{ Gaya \textsc{Benane} \\ 171 avenue de Luminy \\ 13~009~\textsc{Marseille} }}
\signature{ { Gaya \textsc{Benane} } }
\lieu{ \textsc{Marseille} }
\nofax
\date{\today}
\telephone{{ +33~(0)~668~056~437 }}
\email{\href{mailto:gaya.benane@outlook.fr}{gaya.benane@outlook.fr}}
    %\vfill
\conc{\textbf{Job application for a Data Scientist position}}
\opening{\hspace{1em} Dear Hiring Manager,}
\hspace{1em}
I am excited to submit my application for the Data Scientist position at \textsc{Probayes} as advertised. My journey through a Ph.D. in Particle Physics, enhanced by a solid foundation in mathematics and physics, has equipped me with a deep analytical mindset and exceptional problem-solving skills.

\hspace{1em}
During my academic and research tenure, I specialized in particle physics, where I mastered statistical analysis, data visualization, and the development of sophisticated simulation models—key competencies for a Data Scientist. My ability to extract patterns and insights from large datasets is directly applicable to the challenges in data science.
My education at École Polytechnique ($\ell$’X), with its rigorous curriculum and focus on innovation, further strengthened my skills in applied mathematics and computer science. This experience instilled in me a balanced approach of creativity and analytical rigor, crucial for advancing in artificial intelligence.

At \textsc{Probayes}, I am eager to contribute to your mission of bridging research with industry applications in data science. Your diverse projects across sectors such as automotive, defense, and healthcare, promise a dynamic and stimulating work environment. I am particularly excited to leverage my background in physics and mathematics, along with my programming expertise in \texttt{Python}, \texttt{C}, and \texttt{C++}, to develop innovative AI solutions that enhance business outcomes.
\hspace{1em}
I look forward to discussing how my background, skills, and passion align with the needs of your team. Thank you for considering my application. I am enthusiastic about the possibility to become an actif member, with significant contributions to \textsc{Probayes}.
\closing{\hspace{1em}
I look forward to discussing how my background, skills, and passion align with the needs of your team. Thank you for considering my application. I am enthusiastic about the possibility to become an actif member, with significant contributions to \textsc{Probayes}.}
\end{letter}
\end{document}
